``Interestingness'' in Mathematical Theory Exploration

### 2018-09-12 PhDThesis/background_haskell.tex
Thesis changes (e.g. lit review)

\item The existence of theory exploration systems such as \hspec{}, and related
  tools which we can to re-use, including conjecture generators like \qspec{}
  and \speculate{}; counterexample finders like \qcheck{}, \textsc{SmallCheck},
  \textsc{SmartCheck}, \textsc{LeanCheck}, \textsc{Hedgehog}, etc.; theorem
  provers like \textsc{Hip} \cite{rosen2012proving}; and other related testing
  and term-generating systems like \textsc{MuCheck} \cite{le2014mucheck},
  \textsc{MagicHaskeller}~\cite{katayama2011magichaskeller} and
  \textsc{Djinn}~\cite{augustsson2005djinn}.

>>>>

\item The existence of theory exploration systems such as \hspec{}, and related
  tools which we can to re-use, including conjecture generators like \qspec{}
  and \textsc{Speculate}; counterexample finders like \qcheck{}, \textsc{SmallCheck},
  \textsc{SmartCheck}, \textsc{LeanCheck}, \textsc{Hedgehog}, etc.; theorem
  provers like \textsc{Hip} \cite{rosen2012proving}; and other related testing
  and term-generating systems like \textsc{MuCheck} \cite{le2014mucheck},
  \textsc{MagicHaskeller}~\cite{katayama2011magichaskeller} and
  \textsc{Djinn}~\cite{augustsson2005djinn}.
